---
title: "LabExercise2"
author: "Ann Margaret Camayodo"
date: "2024-03-07"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


install.packages("dplyr")
install.packages("rvest")
install.packages("httr")
install.packages("polite")

SCRAPING FOR 50



Movie 1
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie1 <- data.frame()

for (page in 1:5) {
  link1 <- paste0("https://www.imdb.com/title/tt5123896/reviews/?ref_=tt_ql_2", page)
  session1 <- bow(link1, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session1) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName1 <- "Scream, Queen! My Nightmare on Elm Street"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie1 <- rbind(movie1, data.frame(
    movie_name = MovieName1,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}

#View(movie1)

```

Movie 2
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie2 <- data.frame()

for (page in 1:5) {
  link2 <- paste0("https://www.imdb.com/title/tt0111161/reviews/?ref_=tt_ql_2", page)
  session2 <- bow(link2, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session2) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName2 <- "The Shawshank Redemption (1994)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie2 <- rbind(movie2, data.frame(
    movie_name = MovieName2,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie2)

```


Movie 3
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie3 <- data.frame()

for (page in 1:5) {
  link3 <- paste0("https://www.imdb.com/title/tt0050083/reviews/?ref_=tt_ql_2", page)
  session3 <- bow(link3, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session3) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName3 <- "12 Angry Men (1957)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie3 <- rbind(movie3, data.frame(
    movie_name = MovieName3,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie3)

```

Movie 4
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie4 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt6334354/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName4 <- "The Suicide Squad (2021)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie4 <- rbind(movie4, data.frame(
    movie_name = MovieName4,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie4)

```

Movie 5
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie5 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0047478/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName5 <- "Seven Samurai (1954)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie5 <- rbind(movie5, data.frame(
    movie_name = MovieName5,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie5)

```

Movie 6
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie6 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0120689/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName6 <- "The Green Mile (1999)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie6 <- rbind(movie6, data.frame(
    movie_name = MovieName6,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie6)

```

Movie 7
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie7 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0118799/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName7 <- "Life Is Beautiful (1997)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie7 <- rbind(movie7, data.frame(
    movie_name = MovieName6,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie7)

```

Movie 8
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie8 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0245429/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName8 <- "Spirited Away (2001)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie8 <- rbind(movie8, data.frame(
    movie_name = MovieName8,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie8)

```

Movie 9
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie9 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0088763/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName9 <- "Back to the Future (1985)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie9 <- rbind(movie9, data.frame(
    movie_name = MovieName9,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie9)

```

Movie 10
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie10 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt9362722/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName10 <- "Spider-Man: Across the Spider-Verse (2023)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie10 <- rbind(movie10, data.frame(
    movie_name = MovieName10,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie10)

```

Movie 11
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie11 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0172495/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName11 <- "Gladiator (2000)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie11 <- rbind(movie11, data.frame(
    movie_name = MovieName11,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie11)

```

Movie 12
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie12 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0054215/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName12 <- "Psycho (1960)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie12 <- rbind(movie12, data.frame(
    movie_name = MovieName12,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie12)

```

Movie 13
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie13 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0047396/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName13 <- "Rear Window (1954)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie13 <- rbind(movie13, data.frame(
    movie_name = MovieName13,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie13)

```

Movie 14
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie14 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0056058/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName14 <- "Harakiri (1962)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie14 <- rbind(movie14, data.frame(
    movie_name = MovieName14,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie14)

```

Movie 15
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie15 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt1345836/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName15 <- "The Dark Knight Rises (2012)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie15 <- rbind(movie15, data.frame(
    movie_name = MovieName15,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie15)

```

Movie 16
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie16 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0114709/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName16 <- "Toy Story (1995)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie16 <- rbind(movie16, data.frame(
    movie_name = MovieName16,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie16)

```

Movie 17
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie17 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0091251/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName17 <- "Come and See (1985)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie17 <- rbind(movie17, data.frame(
    movie_name = MovieName17,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie17)

```

Movie 18
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie18 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0091251/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName18 <- "Come and See (1985)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie18 <- rbind(movie18, data.frame(
    movie_name = MovieName18,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie18)

```

Movie 19
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie19 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0120815/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName19 <- "Saving Private Ryan (1998)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie19 <- rbind(movie19, data.frame(
    movie_name = MovieName19,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie19)

```

Movie 20
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie20 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0120815/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName20 <- "Saving Private Ryan (1998)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie20 <- rbind(movie20, data.frame(
    movie_name = MovieName20,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie20)

```

Movie 21
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie21 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0407887/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName21 <- "The Departed (2006)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie21 <- rbind(movie21, data.frame(
    movie_name = MovieName21,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie21)

```

Movie 22
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie22 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0047396/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName22 <- "Rear Window (1954)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie22 <- rbind(movie22, data.frame(
    movie_name = MovieName22,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie22)

```

Movie 23
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie23 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0405094/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName23 <- "The Lives of Others (2006)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie23 <- rbind(movie23, data.frame(
    movie_name = MovieName23,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie23)

```

Movie 24
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie24 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0032553/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName24 <- "The Great Dictator (1940)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie24 <- rbind(movie24, data.frame(
    movie_name = MovieName24,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie24)

```

Movie 26
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie25 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0082096/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName25 <- "The Boat (1981)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie25 <- rbind(movie25, data.frame(
    movie_name = MovieName25,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie25)

```

Movie 26
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie26 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0112573/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName26 <- "Braveheart (1995)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie26 <- rbind(movie26, data.frame(
    movie_name = MovieName26,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie26)

```

Movie 27
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie27 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0361748/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName27 <- "Inglourious Basterds (2009)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie27 <- rbind(movie27, data.frame(
    movie_name = MovieName27,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie27)

```

Movie 28
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie28 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0338013/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName28 <- "Eternal Sunshine of the Spotless Mind (2004)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie28 <- rbind(movie28, data.frame(
    movie_name = MovieName28,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie28)

```

Movie 29
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie29 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt2380307/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName29 <- "Coco (I) (2017)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie29 <- rbind(movie29, data.frame(
    movie_name = MovieName29,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie29)

```

Movie 30
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie30 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt8267604/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName30 <- "Capernaum (2018)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie30 <- rbind(movie30, data.frame(
    movie_name = MovieName30,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie30)

```

Movie 31
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie31 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0180093/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName31 <- "Requiem for a Dream (2000)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie31 <- rbind(movie31, data.frame(
    movie_name = MovieName31,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie31)

```

Movie 32
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie32 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0105236/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName32 <- "Reservoir Dogs (1992)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie32 <- rbind(movie32, data.frame(
    movie_name = MovieName32,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie32)

```

Movie 33
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie33 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0993846/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName33 <- "The Wolf of Wall Street (2013)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie33 <- rbind(movie33, data.frame(
    movie_name = MovieName33,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie33)

```

Movie 34
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie34 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0055630/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName34 <- "Yojimbo (1961)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie34 <- rbind(movie34, data.frame(
    movie_name = MovieName34,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie34)

```

Movie 35
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie35 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt7286456/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName35 <- "Joker (I) (2019)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie35 <- rbind(movie35, data.frame(
    movie_name = MovieName35,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie35)

```

Movie 36
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie36 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt10272386/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName36 <- "The Father (I) (2020)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie36 <- rbind(movie36, data.frame(
    movie_name = MovieName36,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie36)

```

Movie 37
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie37 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0086190/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName37 <- "Star Wars: Episode VI - Return of the Jedi (1983)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie37 <- rbind(movie37, data.frame(
    movie_name = MovieName37,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie37)

```

Movie 38
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie38 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0052357/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName38 <- "Vertigo (1958)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie38 <- rbind(movie38, data.frame(
    movie_name = MovieName38,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie38)

```

Movie 39
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie39 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0086250/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName39 <- "Scarface (1983)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie39 <- rbind(movie39, data.frame(
    movie_name = MovieName39,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie39)

```

Movie 40
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie40 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt1049413/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName40 <- "Up (2009)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie40 <- rbind(movie40, data.frame(
    movie_name = MovieName40,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie40)

```

Movie 41
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie41 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0108052/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName41 <- "Schindler's List"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie41 <- rbind(movie41, data.frame(
    movie_name = MovieName41,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie41)

```


Movie 42
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie42 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0816692/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName42 <- "Interstellar"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie42 <- rbind(movie42, data.frame(
    movie_name = MovieName42,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie42)

```



Movie 43
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie43 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0816692/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName43 <- "Interstellar"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie43 <- rbind(movie43, data.frame(
    movie_name = MovieName43,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie43)

```



Movie 44
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie44 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0050986/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName44 <- "Wild Strawberries"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie44 <- rbind(movie44, data.frame(
    movie_name = MovieName44,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie44)

```


Movie 45
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie45 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0032138/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName45 <- "The Wizard of Oz"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie45 <- rbind(movie45, data.frame(
    movie_name = MovieName45,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie45)

```


Movie 46
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie46 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0119217/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName46 <- "Good Will Hunting"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie46 <- rbind(movie46, data.frame(
    movie_name = MovieName46,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie46)

```


Movie 47
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie47 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt5311514/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName47 <- "Your Name."
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie47 <- rbind(movie47, data.frame(
    movie_name = MovieName47,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie47)

```

Movie 48
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie48 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt5311514/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName48 <- "Your Name."
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie48 <- rbind(movie48, data.frame(
    movie_name = MovieName48,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie48)

```

Movie 49
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie49 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0015324/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName49 <- "Sherlock Jr."
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie49 <- rbind(movie49, data.frame(
    movie_name = MovieName49,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie49)

```

Movie 50
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie50 <- data.frame()

for (page in 1:5) {
  link <- paste0("https://www.imdb.com/title/tt0042192/reviews/?ref_=tt_ql_2", page)
  session <- bow(link, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName50 <- "All About Eve"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("span.display-name-link")[1:10]
  scrapedReview <- scrapeNodes(".collapsable div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
  
movie50 <- rbind(movie50, data.frame(
    movie_name = MovieName50,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating
  ))

 
}



#View(movie50)

```


```{r}
imdbReviews = data.frame();

imdbReviews <- rbind(imdbReviews, movie1, movie2, movie3, movie4, movie5, movie6, movie7, movie8, movie9, movie10, movie11, movie12, movie13, movie14, movie15, movie16, movie17, movie18, movie19, movie20, movie21, movie22, movie23, movie24, movie25, movie26, movie27, movie28, movie29, movie30, movie31, movie32, movie33, movie34, movie35, movie36, movie37, movie38, movie39, movie40, movie41, movie42, movie43, movie45, movie46, movie47, movie48, movie49, movie50)

write.csv(imdbReviews, "movieReviews.csv")

```